Colonies - Compute Continuums across Platforms

### 2023-04-15 paper_2023/paper.tex
wip

To address these challenges, the paper presents an open-source framework called Colonies\footnote{https://github.com/colonyos/colonies}, which facilitates execution of computational workloads across a diverse range of platforms. Colonies enables development of a \emph{decentralized runtime environment}, called a \emph{Colony}, which can effortlessly integrate with any third-party application or other workflow systems.

@@

The long-term vision of the Colonies framework is to offer uninterrupted access to computing resources, without interruptions or limitations, allowing data to flow from one service to another. To establish such seamless compute continuums, the paper introduces Colonies, a \emph{decentralized runtime environment} designed to easily integrate with third-party systems to create a seamlessly integrated computing ecosystem. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where workflows can be decomposed into independent microservices that can easily be integrated with other systems or applications running anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems across platforms.

@@

Colonies can be used to implement a decentralized grid-based compute infrastructure for Earth Observation (EO) workloads across diverse platforms. By wrapping computational EO tasks into Colonies processes, interoperability among platforms can be further enhanced. For instance, it becomes possible to create a broker-based architecture that enables OpenEO applications to submit job specifications indirectly to a Colonies server. These specifications could then be picked up by executors connected to different backend providers. Executors could also be used to automatically provision compute resources. For example, automatically setting up Dask\footnote{https://www.dask.org} clusters, or deploy workflows at HPC systems to handle high-demand EO workloads.

\section{Discussion}
This paper has presented an open-source framework called Colonies, which is designed to streamline execution of computational workloads across platforms. Colonies enable the creation of a \emph{decentralized runtime environment}, called a \emph{Colony}, which serves as an intermediary layer to indirectly control and integrate with other computer systems. Instead of directly connecting different systems together, Colonies allows services or users to publish instructions and then assign these instructions to other services. By chaining instructions together, it becomes possible to execute workloads that can operate seamlessly across different platforms.

@@

While microservices is a powerful design pattern, Colonies goes beyond the conventional microservice model and offers a decentralized microservice architecture that allows microservices to reside anywhere on the Internet. Also, by acting as an intermediary layer, Colonies provides a unified interface to facilitate interaction between these microservices, making it possible to create workflows that span multiple platforms. For instance, Colonies could be used to expose an entire HPC system as a microservice and then connected it to other microservices running in the cloud or IoT devices.

>>>>

To address these challenges, the paper presents an open-source framework called Colonies\footnote{https://github.com/colonyos/colonies}, which facilitates execution of computational workloads across a diverse range of platforms. Colonies enables development of a \emph{distributed runtime environment}, called a \emph{Colony}, which can effortlessly integrate with any third-party application or other workflow systems.

@@

The long-term vision of the Colonies framework is to enable uninterrupted access to computing resources, allowing data to flow from one service to another establishing a seamlessly integrated computing ecosystem. To realize this vision, the paper presents Colonies, a \emph{distributed runtime environment} designed to easily integrate with third-party systems. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable compute continuums.

@@

% Colonies can be used to implement a decentralized grid-based compute infrastructure for Earth Observation (EO) workloads across diverse platforms. By wrapping computational EO tasks into Colonies processes, interoperability among platforms can be further enhanced. For instance, it becomes possible to create a broker-based architecture that enables OpenEO applications to submit job specifications indirectly to a Colonies server. These specifications could then be picked up by executors connected to different backend providers. Executors could also be used to automatically provision compute resources. For example, automatically setting up Dask\footnote{https://www.dask.org} clusters, or deploy workflows at HPC systems to handle high-demand EO workloads.

\section{Discussion}
This paper has presented an open-source framework called Colonies, which is designed to streamline execution of computational workloads across platforms. Colonies enable the creation of a \emph{distributed runtime environment}, called a \emph{Colony}, which serves as an intermediary layer to indirectly control and integrate with other computer systems. Instead of directly connecting different systems together, Colonies allows services or users to publish instructions and then assign these instructions to other services. By chaining instructions together, it becomes possible to execute workloads that can operate seamlessly across different platforms.

@@

While microservices is a powerful design pattern, Colonies goes beyond the conventional microservice model and offers a distributed microservice architecture that allows microservices to reside anywhere on the Internet. Also, by acting as an intermediary layer, Colonies provides a unified interface to facilitate interaction between these microservices, making it possible to create workflows that span multiple platforms. For instance, Colonies could be used to expose an entire HPC system as a microservice and then connected it to other microservices running in the cloud or IoT devices.
